%-----------------------------------------------------
% Resume in Latex
% Author: Vineet Naik
% License : MIT
% Adapted from: https://github.com/aschlesener/resume
%-----------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage{geometry}

\geometry{paper=letterpaper, top=15mm, left=18mm, right=18mm, bottom=20mm}

% set header text and sizing
\fancyhf{}
\fancyhead[L]{Vineet Naik}\fancyhead[R]{Page 2}
\pagestyle{fancy}
\thispagestyle{empty}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \centering
  \vspace{-4pt}\large
}{}{0em}\textbf{}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item{
  {#1}
}
}

% Subheading with one title
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[] % bullet points are escaped using [] after item
  \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} #2 & \textbf{#3} \\
    \textbf{#4} \\
  \end{tabular*}\vspace{-5pt}
}

% This subheading allows for two titles
\newcommand{\resumeSubheadingTwo}[7]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} #2 & \textbf{#3} \\
    \textbf{#4} #5 \\
    \textbf{#6} #7 \\
  \end{tabular*}\vspace{-5pt}
}

% Education subheading
\newcommand{\resumeEducationSubheading}[2]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} \\
    #2 \\
  \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=10pt]}
  \newcommand{\resumeItemListEnd}{\end{itemize}}

% -------------------------------------------
  %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING-----------------

% Centered heading with name, location, and contact info
\begin{center}
  \textbf{\Large Vineet Naik} \\
  Bangalore, India
\end{center}\vspace{-4pt}

% Space for phone number and website link below header
\begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
  {\href{mailto:naikvin@gmail..com}{naikvin@gmail.com} | +91 9820776899} & {\href{https://www.naiquev.in}{Website} | \href{https://github.com/naiquevin}{Github} | \href{https://www.linkedin.com/in/vineetnaik/}{LinkedIn}}
\end{tabular*}\vspace{-6pt}

% HR divider
\rule{\textwidth}{1pt}

% --------SUMMARY------------
\resumeSubHeadingListStart
\item[]{ Seasoned software engineer with 15+ years of experience that
    includes building and maintaining terabyte-scale production
    systems. Strong focus on performance, stability, resiliency,
    observability, and security. Proven track record of building
    high-quality, long lasting solutions. Active open
    source contributor. \\~\\
    Available for part-time or full-time roles, preferably those
    leveraging Rust, PostgreSQL, and/or local-first technologies. }

  \resumeSubHeadingListEnd \vspace{-8pt}

  \rule{\textwidth}{0.2pt}

  % -------------------------------------------

  % --------PROGRAMMING SKILLS------------
  \section{TECHNICAL SKILLS} \vspace{-4pt}
  % Bulleted multi-column list of skills
  \begin{multicols}{2}
    \begin{itemize}[leftmargin=10pt]
    \item Full-stack development \vspace{-8pt}
    \item Databases (operational \& internals) \vspace{-8pt}
    \item Distributed systems \vspace{-8pt}
    \item CD/CI \& automation \vspace{-8pt}
    \item Documentation \vspace{-8pt}
    \item Process standardization \vspace{-8pt}
    \item Code reviews \& Mentoring \vspace{-8pt}
    \item Open source software \vspace{-8pt}
    \end{itemize}
  \end{multicols} \vspace{1pt}

  \resumeSubHeadingListStart
\item[]
  \textbf{Languages}{: Rust, Javascript, Clojure, Python, Bash, Emacs Lisp } \\
  \textbf{Databases}{: PostgreSQL, Yugabyte, SQLite, MongoDB, Redis, Elasticsearch } \\
  \textbf{Other technologies}{: Vue.js, IndexedDB, AWS, Git, Kafka, Containers/VMs, Ansible }
  \resumeSubHeadingListEnd \vspace{1pt}
  % -------------------------------------------

  % -----------EXPERIENCE-----------------
  \section{EXPERIENCE}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Sabbatical/Career break}{}{Oct 2023 - Present}
  {Independent developer}
  \resumeItemListStart

  \resumeItem

  {\href{www.captrice.io}{captrice.io}: A guitar practice app that I'm
    building as a ``passion project'' using Rust (compiled to
    webassembly), Vue.js, PostgreSQL and follows the local-first
    paradigm.}

  \resumeItem

  {Open source contributor in
    \href{https://github.com/cosdata/cosdata}{cosdata} - a vector
    database and AI platform written in Rust. Implemented low-level
    buffered-IO abstraction and metadata filtering functionality in
    HNSW index.}

  \resumeItem

  {\href{https://hint.naiquev.in}{HINT}: A home-inventory tracking app
    that can generate grocery checklists. It's an invite-only app I
    built for myself + family \& friends. Written using Axum (Rust),
    Vue.js and PostgreSQL.}

  \resumeItemListEnd \vspace{8pt}

  \resumeSubheading
  {Helpshift,}{Remote}{Jan 2020 - Sep 2023}
  {Staff engineer, platforms team}
  \resumeItemListStart

  \resumeItem

  {Led the efforts to stabilize and scale a critical PosgreSQL cluster
    after a major outage. Have published a
    \href{https://medium.com/helpshift-engineering/auto-vacuum-tuning-in-postgresql-3408f8b62ad8}{blog
      post} about it. }

  \resumeItem

  {Migration of transactional data from MongoDB to Yugabyte with near
    zero-downtime, unlocking horizontal scaling of writes. Major
    contributions in achieving operational stability of the
    self-hosted Yugabyte cluster.}

  \resumeItem

  {Led migration of multiple PostgreSQL clusters across AWS regions
    with zero-downtime as part of a larger migration project that gave
    us \$2M+ savings per year in AWS bills. Co-authored a
    \href{https://medium.com/helpshift-engineering/migrating-postgresql-databases-using-aws-dms-e91cf26fa6e}{blog
      post} about it.}

  \resumeItemListEnd

  % put a break in page, so job position doesn't wrap pages
  \newpage

  \resumeSubHeadingListEnd

  % properly position header for second page
  \setlength{\headsep}{0.2in}
  \setlength{\headheight}{14pt}

  \resumeSubHeadingListStart

  \resumeSubheading
  {Helpshift,}{Pune,}{Oct 2018 - Dec 2019}
  {Staff engineer, ``Architects'' team}
  \resumeItemListStart
  \resumeItem
  {Foundational work on an extensible framework for integrating Helpshift with external messaging platforms such as Facebook, SMS, Apple business chat, Whatsapp.}
  \resumeItem
  {Proposed, designed, implemented and ensured company-wide adoption of a Clojure framework for gradually modularizing a large monolithic code base, reducing the test suite duration by 20-30\%.}
  \resumeItem
  {Standardization of processes and tooling for platform/architecture reviews, incident reports, change management, on-call workflows.}
  \resumeItem
  {Trained and mentored multiple junior and senior ICs.}
  \resumeItemListEnd \vspace{8pt}

  \resumeSubheading
  {Helpshift,}{Pune,}{Aug 2014 - Oct 2018}
  {Sofware artisan, ``Prodeng'' team}
  \resumeItemListStart
  \resumeItem
  {Major contribution in building a job scheduling platform on top of Jenkins. Spoke about it at Rootconf 2018 (\href{https://youtu.be/Gk0GLQFe4po?si=C6Gv9dv6I3oRrmyJ}{video}). In use as of Sep 2023.}
  \resumeItem
  {Designed, implemented and maintained self-served release automation platform built on top of AWS, ansible, JIRA and Jenkins. In use as of Sep 2023.}
  \resumeItem
  {Custom solution for incremental backups of Apache Kylin data stored in HBase.}
  \resumeItem
  {Implemented and maintained tooling for local/dev setup by reusing the production ansible workflows developed by our devops/infra team.}
  \resumeItemListEnd \vspace{8pt}

  \resumeSubheading
  {Kodeplay,}{Mumbai,}{Jul 2009 - Jul 2014}
  {Technical Lead}
  \resumeItemListStart
  \resumeItem
  {KodeCRM, an interactive chat solution and CRM for ecommerce site owners (dysfunctional).}
  \resumeItem
  {\href{https://github.com/kodeplay/kodelearn}{KodeLearn} - Open source learning management system.}
  \resumeItem
  {Multi-vendor ecommerce and marketplace extension for Opencart.}
  \resumeItem
  {In the initial years, we offered software services as well. Kodeplay was a fully bootstrapped company. I was the first employee.}
  \resumeItemListEnd \vspace{8pt}

  \resumeSubheading
  {Greaves Cotton Ltd.,}{Pune,}{Jul 2007 - Jul 2008}
  {Manufacturing trainee engineer}
  \resumeItemListStart
  \resumeItem
  {During my small stint of 1 year in the manufacturing industry I worked as an assembly line engineer in the first 5 months and then in the Production Planning and Control department for the later months.}
  \resumeItem
  {This was my first job after graduation, before I found interest in the  field of software engineering and computer science.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
  % -------------------------------------------

  % -----------EDUCATION-----------------
  \section{EDUCATION}
  \resumeSubHeadingListStart
  \resumeEducationSubheading
  {Bachelor of Engineering, Mechanical (2003 - 2007)}
  {Rajiv Gandhi Institute of Technology, Mumbai University}
  \resumeSubHeadingListEnd
  % -------------------------------------------

\end{document}
